% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2010 Max Alcala <maxarturo-at-gmail.com> https://maxalcala.com
%
%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.65in}
\setlength{\textwidth}{7.0in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

%-----------------------------------------------------------
%\usepackage{fullpage}
%\textheight=9.0in
\usepackage{fontspec}
\setmainfont{BerkeleyMonoNF-Regular}
\usepackage{shading}
\usepackage{hyperref}
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-3pt}}
\newcommand{\resheading}[1]{{\large {\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\thinline}{\line(1,0){450}}
\newcommand{\addline}{\noindent\rule{\textwidth}{2pt}}
\newcommand{\ressubheading}[4]{
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \MakeUppercase{#2} \\
			\textit{#3} & #4 \\
	\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}


% \vspace{1pt}
% VER-1717707387000


\begin{tabular*}
	{7in}{l@{\extracolsep{\fill}}r}

  \textbf{\Large{MAX ARTURO ALCAL\'{A} S\'{A}INZ}} & |> 727931187386

\end{tabular*}

\noindent\rule{\textwidth}{2pt}
\vspace{2pt}
\begin{tabular*}
	{7in}{l@{\extracolsep{\fill}}r}
	
    \MakeUppercase{140 48th St SE} &  	 https://github.com/maxArturo \\
     \MakeUppercase{Paris, TX 75462 USA}				&	  	maxarturo@gmail.com  \\
  TEL: (+1) 469-893-0681                          &     https://maxalcala.com \\
\end{tabular*}

 \addline
 
 \begin{center}
 \resheading{SUMMARY}
 
   Software engineer with business and customer-facing experience in both Fortune 50 companies and startups. My experience has ranged from individual contributor (including a Principal role), to managing large teams onshore and offshore.  My current interests cover language parsers/compilers, literate programming, and the art of fostering a healthy company culture.
 
 \end{center}
 
\addline

%-----------------------------------------------------------
%Skills

\resheading{SKILLS}

\vspace{2pt}
\textit{NOTE}: The following list of technologies and languages is not exhaustive nor comprehensive for practicality; please reach out if a particular language or framework matters to you.
\begin{description}
	\item[PROGRAMMING LANGUAGES:]
    TS/ES7/ESNext/JS, Kotlin, Ruby, Golang, Common Lisp, Rust, Dart, VBA/VBS, sh/bash/zsh, \LaTeX, most markup and hypertext languages. 

	\item[FRAMEWORKS AND STORAGE:]
    GraphQL, message queues, Rails, NextJS/most JS frameworks, Reactive Extensions (particularly Rx.js). Varied functional programming experience (Haskell, Elm, functional TS libraries). RDBMS/NoSQL/K-V/Columnar persisted storage, as well general caching components and libraries.

	\item [DEVOPS/CI:]
    Jenkins/Teamcity/GH actions, deployments via Docker and containerization, Kubernetes/istio. AWS/GCP/Azure management, cost tuning and other general tasks (IAM, TF/deployment troubleshooting), etc. Instrumentation and measurement, bash scripting and basic Linux server management. Previous Terraform/Chef exposure. Automated testing/e2e via Playwright/Cypress/Puppeteer.

  \item [FRONTEND/MOBILE:]
    HTML5, CSS preprocessors, Javascript/precompilers (Babel/TypeScript). Mobile primarily via Flutter. Client-side data visualization and processing (d3, crossfilter, SVGs), Remix framework, React.js, Redux, Angular 6/7/8. No-JS frameworks (HTMX, tachyons.css)

	\item[MANAGEMENT/PE/TECH LEAD:]
    Work at any level of abstraction within management (process requirements, deliverables, proof-of-concept). Excellent analytical, communication and problem-solving skills. Seasoned interviewer and hiring manager. Previous experience working directly with Fortune 50 VPs as well as directly with end-users. Experienced leading offshore, as well as onshore teams.

	\item[NATURAL LANGUAGES:]
    Native English, Native Spanish, Intermediate Japanese {\fontspec{IPAMincho}（日本語能力試験N3)}

	\item[CERTIFICATIONS:]
		AWS Certified Solutions Architect - Associate

\end{description}

\pagebreak
\addline

%-----------------------------------------------------------
%Experience
\resheading{EXPERIENCE}
\begin{itemize}

\item
  \ressubheading{Common Sense Privacy (Subsidiary of Common Sense Media\texttrademark)}{Remote}{Lead Contractor}{2023 - Present}
	\begin{itemize}
    \resitem{Lead developer for company's codebases}
    \resitem{Took over from previous contractor team at a critical junction and refactored code for maintainability}
    \resitem{Implemented CI/CD best practices, ensured test reliability, upgraded dependencies and enabled streamlined long-term support}
    \resitem{Current approach allows feature growth in balance with reliability at a fraction of the budget}
		\resitem{Stack: Vite/Typescript, Remix framework, Node.js, AWS, Docker, CircleCI, MySQL}
	\end{itemize}
  \thinline

\item
  \ressubheading{PriceWaterhouseCoopers, LLC (PwC)}{Chicago, IL}{PwC Labs – Principal Engineer}{2021 - 2023}
	\begin{itemize}
    \resitem{Led design and implementation of blockchain auditing solutions for PwC Labs}
    \resitem{Provided technical leadership, executed on mission-critical components and prioritized projects with senior leadership}
		\resitem{Spearheaded blockchain research, PoC and upskilling via hands-on seminars}
		\resitem{Support and mentor offshore developers. Encouraged best practices, industry-standard patterns, and performed architectural analysis}
		\resitem{Stack: ES6/Typescript, Angular 5, Node.js, GCP Suite, Docker, Kubernetes, Firebase, Jenkins, Postgres}
	\end{itemize}
  \thinline

\item
  \ressubheading{\href{https://clearcover.com}{Clearcover.com}}{Chicago, IL}{Lead Software Engineer}{2019 - 2021}
	\begin{itemize}
    	\resitem{Lead team responsible for successfully delivering the company's core Policy Management API}
    	\resitem{Build templating system for generating insurance forms via AWS/Puppeteer/Node apis}
		\resitem{Pair, upskill, and unblock team members to maximize their productivity and promote a healthy dev team culture}
		\resitem{Stack: Functional Typescript(v3.x), Rails, Kotlin, AWS/K8s, Postgres}
	\end{itemize}
  \thinline

\item
  \ressubheading{PriceWaterhouseCoopers, LLC (PwC)}{Chicago, IL}{New Ventures Practice – Tech Lead}{2017 - 2019}
	\begin{itemize}
    \resitem{Provide technical leadership for multiple greenfield SaaS offerings across all aspects of the SDLC}
		\resitem{Responsible for all aspects of technical execution for product vision: Architecture, hands-on development, infrastructure, code quality/best practices, hiring, runbooks, etc.}
		\resitem{Lead offshore developers with a supportive environment, mentoring and industry-standard patterns}
		\resitem{Promote successful development team behaviors (developer-led estimations, people over process) in the firm}
		\resitem{Stack: ES6/Typescript, Angular 5, Node.js, GCP Suite, Docker, Kubernetes, Firebase, Jenkins, Postgres}
	\end{itemize}
  \thinline
    

\item
  \ressubheading{ReviewTrackers}{Chicago, IL}{Senior Software Developer}{2017}
	\begin{itemize}
    \resitem{Deliver features across the entire stack to unlock company growth}
    \resitem{Support team efficiency by automating tasks and workflows}
    \resitem{Pair-program and mentor junior developers}
    \resitem{Measure performance and find optimization solutions}
        \resitem{Stack: React, Golang. Ruby, Solr, Heroku/AWS, React, Node.js, Postgres}
	\end{itemize}

% \pagebreak
\item
  \ressubheading{Shoppertrak}{Chicago, IL}{Senior Software Developer/Team Lead}{2015 - 2016}
	\begin{itemize}
    \resitem{Own and maintain the Node API for the company's main reporting app }
    \resitem{Manage the tasks for my team and prioritize with PMs and Tech Architect}
    \resitem{Promote best practices in my team, pair-program and mentor teammates}
    \resitem{Configure CI tools, provision, deploy and document server infrastructure requirements}
     \resitem{Stack: Angular, Node.js, AWS, Redshift/PG, TeamCity}
	\end{itemize}
  \thinline
    

% \newpage

\item
	\ressubheading{Tukaiz, LLC}{Chicago, IL}{Software Developer}{May - Oct 2015}
	\begin{itemize}
		\resitem{Support Rails 2.3.8, 3, \& 4 applications }
		\resitem{Refactored large legacy VB codebase into Ruby}
		\resitem{Re-implemented file management scheduler with Rails/Sidekiq}
	\end{itemize}
  \thinline
    

\item 
	\ressubheading{Gearbox Software}{Dallas, TX}{Software Developer - Contractor}{May - Dec 2015}
	\begin{itemize}
		\resitem{Implement Battleborn Game launch and Beta registration sites with Ruby/Rails}
		\resitem{Collaborate on UX flows and internal API flow}
	\end{itemize}

\end{itemize}
\addline
\\
\resheading{EDUCATION}
\begin{itemize}
\item
	\ressubheading{M.S. Supply Chain Management}{GPA: 3.72}
{University of Texas at Dallas}{Dec 2012}

\item
	\ressubheading{B.S. Operations Management, Minor in Computer Science}
		{GPA: 3.94}{University of Texas at Dallas: Summa Cum Laude, Dean's
			List}{Dec 2011}

\item
	\ressubheading{Donnguk University-Seoul, South Korea}{March-Jun 2010}{MIS
		Exchange Program}{GPA: 3.95}
\end{itemize}



\pagebreak
%-----------------------------------------------------------
%Projects
\addline
\\
\resheading{PROJECTS AND OSS}
\begin{description}
  \item [Vamonos MGP:] A flutter ios/Android app to assist the general public in the Pueyrredón municipality of Argentina with public transportation arrival times. 

	\item [maxarturo.github.io:] A barebones static site generator that aims for dependency reduction and speed of generation, while presenting a literate hypertext in the style of Edward Tufte. \href{https://github.com/maxArturo/maxarturo.github.io}{hosted under maxalcala.com}
	
  \item [cl-peg-yapp:] Product Expression Grammar (PEG) parser, code generator and meta-parser built from first principles in SBCL. Parses its own grammar and allows for PEG bottom-up testing and literate coding. \href{https://github.com/maxArturo/cl-peg-yapp}{link}

  \item [zod:] Collaborated on the GH project. A versatile TS run-time type validator. \href{https://github.com/colinhacks/zod}{gh link} and \href{https://github.com/colinhacks/zod/commits?author=maxArturo}{commits}

	\item [jibun (WIP):] An efficient, linear-time \href{https://en.wikipedia.org/wiki/Hitori}{Hitori} puzzle generator, with a React frontend. It improves upon the state-of-the-art with a novel graph algorithm to generate covered squares, and Knuth's DLX exact-cover algorithm to generate numbers.

\end{description}

%\newpage
\end{document}
